Condensed Matter Field Theory notes

### 2017-03-06 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] Add a brief Summary of Quantum double well for Condensed Matter Field Theory.

\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\printnomenclature
\section{A brief Summary of Quantum double well}

The Quantum double well:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/quantum-double-well.png}
    \caption{Quantum double well}
    The solid line is the double well potential. The dotted line in
    the second quarter is to remind us of the single well potential and its sets
    of eigenvalues. The inverted potential in Euclidean time is shown below the
    $q$-axis.
\end{figure}
The Euclidean path integral is
\begin{equation}
    G_E(a,\pm a:\tau)=\int_{q(0)=\pm a,q(\tau)=a} Dq\,
    \exp(-\frac{1}{\hbar}\int_0^\tau\dd{\tau'}
        \left(\frac{m}{2}\dot{q}^2+V(q)\right)
    )
\end{equation}
with the imaginary time saddle point equation
\begin{equation}
    -m\ddot{q}+V'(q) = 0
\end{equation}

It is turned into several contributions:
\begin{equation}
    A = A_{cl}\times A_{qu}
\end{equation}
where $A$ denotes transition amplitude, "cl" for classical, "qu" for quantum.

The classical contribution includes a stationary not moving part $A_{cl,st}$, a
moving but bouncing back and forth in the inverted potential part $A_{cl,inst}$.
The moving and bouncing back and forth motion is termed \nomen{instanton}, see
p.117(\cite{Altland2010}) for details.

The $A_{cl,st}$ is $e^{0}=1$ since the stationary path $q\equiv0$. The
$A_{cl,inst}$ is calculated in the book (pp.116-117), and the result is:
\begin{equation}
    A_{cl,inst,one-trip} = \exp(-\frac{1}{\hbar}S_{inst})
\end{equation}
for one bouncing trip. Here $S_{inst}$ is given by eq.3.36 in p.117. Adding them
together gives:
\begin{equation}
    A_{cl,inst} =
    \sum_{n\text{ even/odd}}^\infty \frac{1}{n!}
    \left(\tau K e^{-S_{inst}/\hbar}\right)^n
    =\cosh(\tau Ke^{-S_{inst}/\hbar})\text{ or }\sinh(\tau Ke^{-S_{inst}/\hbar})
\end{equation}

where $K$ is just some prefactor explained in p.118 and calculated in
pp.122-123.

The quantum contribution is due to the fluctuation of path around the classical
path. This part is also divided into two categories. The $A_{qu,st}$ for
fluctuation around the stationary path is calculated in the section about single
well green function, spcifically eq.3.31 in p.114. It is approximated in p.119
to be
\begin{equation}
    A_{qu,st,n} = e^{-\omega(\tau_{i+1}-\tau_i)/2}
\end{equation}
and adding together gives
\begin{equation}
    A_{qu,st}= \prod_i e^{-\omega(\tau_{i+1}-\tau_i)/2} = e^{-\tau\omega}
\end{equation}
The rest $A_{qu,inst}$ from fluctuation around instanton is assumed to be
negligible (p.119).

In summary:
\begin{table}[H]
    \centering
    \begin{tabular}{l c c}
        Path       & Classical ($0$th order) & Fluctuation ($2$nd order) \\
        Stationary & $1$                     & $\approx e^{-\omega\tau}$  \\
        Instanton  & $e^{-\frac{1}{\hbar}S_{\text{inst}}}$, or $\cosh(\tau Ke^{-S_{\text{inst}}/\hbar}) \sinh(\tau Ke^{-S_{\text{inst}}/\hbar})$ & $\approx 1$\\
    \end{tabular}
\end{table}

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
